---
title: "p8105_hw5_mp3653"
author: "Matthew Perrotta"
date: "November 8, 2018"
output: github_document
---

### Load Libraries
```{r}
library(tidyverse)
```
#Problem 1
Create Dataset with file names
```{r}
#file paths and file names
study = tibble(file_path = list.files('./data/', pattern = '*.csv', full.names = TRUE), file_name = basename(file_path))
```

Creating function to read in data
```{r}
read_data = function(data){
  
  read_csv(file = data)
  
}
```

Read in the data
```{r}
study_data = study %>%
  mutate(obs = map(file_path, read_data))
```

Tidy data
```{r}
study_data = study_data %>% 
  unnest() %>% 
  janitor::clean_names() %>% 
  gather(key = week, value = value, week_1:week_8) %>% 
  mutate(id = str_replace(file_name, '.csv',''),
         week = as.numeric(str_replace(week, 'week_', ''))) %>% 
  separate(id, into = c('group', 'id'), sep = '_') %>% 
  mutate(group = str_replace(group, 'con', 'control'),
         group = str_replace(group, 'exp', 'exposed')) %>% 
  select(-file_path, -file_name)
```

### Spaghetti plot of data
```{r}
study_data %>% 
  ggplot(aes(x = week, y = value, color = id)) +
  geom_line() +
  facet_grid(~group) +
  labs(
    title = 'Exposed vs. Control Over 8 Week Period'
  )
```
Over the 8 week period, there is a general increase in values for the exposed group while for the control group the values remain relatively the same.


# Problem 2
### Import and Clean Data
```{r}
homicide_data = read_csv('https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv') %>%
  janitor::clean_names() %>% 
  unite(city_state, c(city, state), sep = ", ", remove = FALSE)
```

The `homicide_data` dataset contains `r nrow(homicide_data)` rows of observations for `r nrow(distinct(homicide_data, city))` US cities. There are `r ncol(homicide_data)` variables in the dataset, giving the date of the event, victim info (name, race, age, and sex), and location (city, state, and long + lat). There is also a variable `disposition` describing the current status of the investigation into the homicide.

Total number of homicides and unsolved homicides
```{r}
homicide_data_new = homicide_data %>% 
  group_by(city_state) %>% 
  mutate(total_homicides = n()) %>% 
  filter(disposition %in% c('Closed without arrest', 'Open/No arrest')) %>%
  mutate(unsolved_homicides = n()) %>% 
  select(city_state, unsolved_homicides, total_homicides) %>% 
  distinct()
```

proportion of unsolved murders in Baltimore
```{r}
baltimore = homicide_data_new %>% 
  filter(city_state == 'Baltimore, MD')

prop_baltimore = prop.test(baltimore[[2]], baltimore[[3]]) %>% 
  broom::tidy() %>%  
  select(estimate, conf.low, conf.high)

prop_baltimore
```

estimates anf CI's for all cities
```{r}
prop = function(unsolved, total){
  
  prop.test(unsolved, total) %>% 
    broom::tidy() %>%  
    select(estimate, conf.low, conf.high)
    
}

prop_cities = homicide_data_new %>% 
  mutate(prop = map2(unsolved_homicides, total_homicides, prop)) %>% 
  unnest() %>% 
  ungroup()
```

plot of estimates and CI's for all cities
```{r}
prop_cities %>% 
  mutate(city_state = as.factor(city_state)) %>% 
  mutate(city_State = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(
    title = 'Estimated Proportion of Unsolved Murders with Confidence Intervals'
  )
```

